taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-08-28 paper/manuscript.Rmd
Flesh out unresovled names section.

Databases of taxonomic names such as the Integrated Taxonomic Information System [ITIS; @itis], the National Center for Biological Information's (NCBI) Taxonomy database, [@ncbi], the Catalogue of Life [COL; @col], and over one hundred other providers have sought to address these problems by providing expert-curated lists of accepted taxonomic names, synonyms, associated taxonomic rank, hierarchical classification, and scientific authority (e.g. author and date) establishing a scientific name.
The R language [@R] is widely used in ecology and evolution [@Lai2019] and the `taxize` package [@Chamberlain2013] has become a popular way R users to interact with naming providers and name resolution services.  `taxize` implements bindings to the web APIs (Application Programming Interface) hosted by many popular taxonomic name providers. Unfortunately, this means that functions in the `taxize` are impacted by several major drawbacks that are inherent in the implementation of these central API servers, such as:

@@

potential ways for resolving unidentified names
* multiple hits from `get_ids()` check duplicates, use `by_`
* typo
* formatting issues (be careful about false matches), `clean_names()`
* ambiguous resolution, explore with `synonyms()` (these are the same concept with different names or vice versa)

The spirit of taxadb is not to automate steps that require expert knowledge, but provide access to multiple potential "taxonomic theories"

>>>>

Databases of taxonomic names such as the Integrated Taxonomic Information System [ITIS; @itis], the National Center for Biological Information's (NCBI) Taxonomy database, [@ncbi], the Catalogue of Life [COL; @col], and over one hundred other providers have sought to address these problems by providing expert-curated lists of accepted taxonomic names, synonyms, associated taxonomic rank, hierarchical classification, and scientific authority (e.g. author and date) establishing a scientific name.
The R language [@R] is widely used in ecology and evolution [@Lai2019] and the `taxize` package [@Chamberlain2013] has become a popular way for R users to interact with naming providers and name resolution services.  `taxize` implements bindings to the web APIs (Application Programming Interface) hosted by many popular taxonomic name providers. Unfortunately, this means that functions in the `taxize` are impacted by several major drawbacks that are inherent in the implementation of these central API servers, such as:

@@

`get_ids` offers a first pass at matching scientifc names to id, but names may remain unresolved for a number of reasons. First, a name may match to multiple accepted names, as in the case of a species that has been split. By design, these cases are left to be resolved by the researcher using the 'by_' functions to filter underlying taxonomic tables for additional information. A name may also be unresolved due to typos or improper formatting. `clean_names` addresses common formatting issues such as the inclusion of missing species epithets (e.g. `Accipiter sp.`) that prevent matches to the Genus, or intraspecific epithet such as `Colaptes auratus cafer` that prevent matches to the bionmial name. These modifications are not appropriate in all settings and should be used with care (Language from vignette).

Names may also have an ambiguous resolution *discussion about taxonomic concepts here*. The spirit of taxadb is not to automate steps that require expert knowledge, but provide access to multiple potential "taxonomic theories".
